Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-02 doc/prelim/presentation/prelim_presentation.tex
updated solution evolution captions

  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{1.25}{ \input{orthogonal_residual.pdftex_t} }
    \end{center}
    \caption{\textbf{Orthogonality constraint of the new residual with
        respect to $\mathcal{L}$.} }
  \end{figure}

@@

  \begin{itemize}
  \item For GMRES:
  \end{itemize}
  \[
  \mathcal{L} = \ve{A} \mathcal{K}_m(\ve{A},\ve{r}_0)
  \]

@@

  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{0.75}{ \input{partitioned_matrix.pdftex_t} }
    \end{center}
    \caption{\textbf{Matrix-vector multiply $\ve{A}\ve{x}=\ve{y}$
        operation on 3 processors.}
      \label{fig:partitioned_matvec_multiply} }
  \end{figure}

  \pause
  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{0.75}{ \input{matvec_proc_1.pdftex_t} }
    \end{center}
    \caption{\textbf{Components of multiply operation owned by process
        1.} }
    \label{fig:matvec_proc_1}
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=4in]{direct_100.png}
    \end{center}
    \caption{\textbf{Direct solution to Poisson Equation.}
      \textit{1000 histories per state, \sn{2.5}{5} total
        histories. 54.7 seconds CPU time.} }
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=4in]{direct_1000.png}
    \end{center}
    \caption{\textbf{Direct solution to Poisson Equation.} \textit{100
        histories per state, \sn{2.5}{6} total histories. 644 seconds
        CPU time.} }
  \end{figure}

>>>>

  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{1.1}{ \input{orthogonal_residual.pdftex_t} }
    \end{center}
    \caption{\textbf{Orthogonality constraint of the new residual with
        respect to $\mathcal{L}$.}}
  \end{figure}

@@

  \begin{itemize}
  \item For GMRES (Saad, 1986):
  \end{itemize}
  \[
  \mathcal{L} = \ve{A} \mathcal{K}_m(\ve{A},\ve{r}_0)
  \]

@@

  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{0.6}{ \input{partitioned_matrix.pdftex_t} }
    \end{center}
    \caption{\textbf{Matrix-vector multiply $\ve{A}\ve{x}=\ve{y}$
        operation on 3 processors.}
      \label{fig:partitioned_matvec_multiply} }
  \end{figure}

  \pause
  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{0.7}{ \input{matvec_proc_1.pdftex_t} }
    \end{center}
    \caption{\textbf{Components of multiply operation owned by process
        1.} }
    \label{fig:matvec_proc_1}
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=4in]{direct_100.png}
    \end{center}
    \caption{\textbf{Direct solution to Poisson Equation.}
      \textit{100 histories per state, \sn{2.5}{5} total
        histories. 54.7 seconds CPU time.} }
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=4in]{direct_1000.png}
    \end{center}
    \caption{\textbf{Direct solution to Poisson Equation.} \textit{1000
        histories per state, \sn{2.5}{6} total histories. 644 seconds
        CPU time.} }
  \end{figure}
